Time-series modeling of epidemics in complex populations: detecting changes in incidence volatility over time

### 2025-01-08 ms-3/ms.tex
add text

@@

>>>>

Since very large $\theta$ correspond to processes that are close to a Poisson process, the test will not produce a p-value if any of the three values are greater than 1/(1e-3). 
Very large $\theta$ estimates are often produced in small populations when the process can't be distinguished from a Poisson process. Therefore, we have very small $\phi = 1/\theta$  values be considered zero, at which point we fail to reject the Poisson hypothesis.

In addition, we imposed restrictions on $\theta$ estimates such that $\theta = 0$ (point mass) results in no p-value being produced in the test result. So, large $\phi$ are considered values where we fail to reject the point mass hypothesis.

Additionally, we included an option to retrieve the likelihood of a range of theta values in addition to these restrictions.

@@

Our simulation samples start points and theta values, and incidence is modeled according to overall incidence trends.
